Ordinal regression models made easy. A tutorial on parameter interpretation, data simulation, and power analysis.

### 2024-01-30 paper/paper.Rmd
update

---
title             : "Ordinal regression models made easy. A tutorial on parameter interpretation, data simulation, and power analysis."
shorttitle        : "Ordinal regression models made easy"
author: 
  - name          : "Filippo Gambarota"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Via Venezia 8, 35131, Padova (Italy)"
    email         : "filippo.gambarota@unipd.it"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Methodology"
      - "Software"
  - name          : "Gianmarco Altoè"
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Writing - Review & Editing"
      - "Supervision"
affiliation:
  - id            : "1"
    institution   : "Department of Developmental Psychology and Socialization, University of Padova, Italy"
abstract: |
  Ordinal data are very common in psychology such as Likert items, ratings or generic ordered variables. Despite the widespread, these variables are usually analyzed using metric models (e.g., standard linear regression). This approach can have important drawbacks in terms of statistical inference (e.g., reduced power and increased type-1 error) and prediction. One of the possible reason of not using ordinal regression models could be the difficulty in understanding parameters (e.g., odds ratios) or conduting a power analysis. The aim of the tutorial is presenting ordinal regression models using a simulation-based approach. In the first section we introduced the general model highlighting the crucial components and assumptions. Then we explained how to intepret the parameters for a logit and probit model. Then we proposed two way for simulating ordinal data as a function of predictors showing common research design such as a 2x2 interaction with categorical predictors and the interaction between a numeric and categorical predictor. Finally, we showed an example of power analysis using simulations that can be easily extended to complex models with multiple predictors. The tutorial is supported by a collection of custom R functions developed to simulate and understand ordinal regression models. The code to reproduce the proposed simulation, the custom R functions and other examples of ordinal regression models can be found on the online Open Science Framework repository ([https://osf.io/93h5j](https://osf.io/93h5j/?view_only=33f262ee28374a88b935f0a25cefdb34)).

keywords          : "ordinal, simulations, power"
wordcount         : "X"
bibliography:
  - "packages.bib"
  - "`r filor::fil()$bib`"
floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
params:
  floatplaceh: true
  preprint: true
classoption       : "man"
output: 
  papaja::apa6_pdf:
    latex_engine: xelatex
    header_includes:
      - \usepackage{booktabs, caption, longtable, colortbl, array, hhline, mathbf}
  papaja::apa6_docx: default
---

@@

We can identify three main models: *cumulative models* [CM, @McCullagh1980-cw; @Agresti2010-rz], *sequential models* [@Tutz1990-fe], and *adjacent category models*. Among these, the CM is the most widely used, assuming the existence of a latent variable categorized using a set of thresholds. The *sequential model* is appropriate when modeling sequential processes where responding to a certain category implies have already reached lower categories. The *adjacent category model* compares a category with the successive one and can be seen  the adjacent-category model can be seen as a series of binomial regressions taking into account the ordering [@Tutz2022-dg].

@@

In this section we introduce some notation for the CM to be consistent with the existing literature and the `ordinal` R package [@Christensen2022-jk]. We define $Y_k$ as the observed ordinal variable with $k$ levels and $Y^\star$ is the underlying latent variable. The latent variable is segmented using $k - 1$ thresholds $\alpha_1, \dots, \alpha_{k - 1}$. Similarly to the generalized linear models framework [e.g., @Fox2015-ps], we define $g(p) = \eta$ as the link function that maps probabilities into the linear predictor $\eta$. To transform back $\eta$ into probabilities we use the inverse of the link function $p = g^{-1}(\eta)$. The specific link function define the type of model and require different R functions. For example, using a Normal distribution (*probit* link function) requires using the cumulative distribution function $g(p) = \Phi^{-1}(p) = \eta$ and the inverse of the link function is the inverse cumulative distribution function (or quantile function) defined $p = g^{-1}(\eta) = \Phi(\eta)$.

@@

In the CM, thresholds $\alpha_k$ are considered fixed and part of the measurement procedure [@Liddell2018-wu; but see the *location-shift* models by @Tutz2022-dg, where thresholds vary as a function of predictors] and can be considered as intercepts. The proposed CM can be parametrized in different ways. @Liddell2018-wu and @Kruschke2015-re proposed a Bayesian version of the model and @Gelman2020-tg proposed other thresholds parametrizations.

@@

For fitting the CM we used the `ordinal` package [@Christensen2019-cz]. The `ordinal` package provide a complete and intuitive way to implement the ordinal models. The syntax is very similar to standard linear models in R with functions to calculate predictions, perform model comparison and extract relevant model information.[^2]

[^2]: For a very complete overview of the ordinal package see @Christensen2019-cz and the Package documentation <https://cran.r-project.org/web/packages/ordinal/ordinal.pdf>

@@

```{r tab-dataset-example-latex, eval = which_output("latex")}
ss |> 
  kable(booktabs = TRUE, format = "latex", caption = filor::get_caption(), escape = FALSE, align = "c", row.names = FALSE) |> 
  kable_styling(full_width = FALSE) |> 
  row_spec(0, bold = TRUE) 
```

@@

```{r fig-effects-num-by-cat-interaction, fig.place = TRUE, fig.width=9, fig.height=9, fig.cap=filor::get_caption()}
# plot(ggpredict(fit, terms = c("x[all]", "g")))
ggpredict(fit, terms = c("x[all]", "g")) |> 
  data.frame() |>
  mutate(response.level = paste("Y = ", response.level)) |> 
  ggplot(aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.3) +
  geom_line(aes(group = group), linewidth = 1) +
  facet_grid(response.level~1) +
  ylab("Probability") +
  mtheme() +
  viridis::scale_fill_viridis(discrete = TRUE)
```

>>>>

---
title             : "Ordinal regression models made easy. A tutorial on parameter interpretation, data simulation, and power analysis."
shorttitle        : "Ordinal regression models made easy"
author: 
  - name          : "Filippo Gambarota"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Via Venezia 8, 35131, Padova (Italy)"
    email         : "filippo.gambarota@unipd.it"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Methodology"
      - "Software"
  - name          : "Gianmarco Altoè"
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Writing - Review & Editing"
      - "Supervision"
affiliation:
  - id            : "1"
    institution   : "Department of Developmental Psychology and Socialization, University of Padova, Italy"
abstract: |
    Ordinal data are widespread in psychology such as Likert items, ratings, or generic ordered variables. These variables are usually analyzed using metric models (e.g., standard linear regression) with important drawbacks in terms of statistical inference (reduced power and increased type-1 error) and prediction. One possible reason for not using ordinal regression models could be difficulty in understanding parameters or conducting a power analysis. The tutorial aims to present ordinal regression models using a simulation-based approach. Firstly, we introduced the general model highlighting crucial components and assumptions. Then we explained how to interpret parameters for a logit and probit model. Then we proposed two ways for simulating data as a function of predictors showing a 2x2 interaction with categorical predictors and the interaction between a numeric and categorical predictor. Finally, we showed an example of power analysis using simulations that can be easily extended to complex models with multiple predictors. The tutorial is supported by a collection of custom R functions developed to simulate and understand ordinal regression models. The code to reproduce the proposed simulation, the custom R functions, and additional examples of ordinal regression models can be found on the online Open Science Framework repository ([https://osf.io/93h5j](https://osf.io/93h5j/?view_only=33f262ee28374a88b935f0a25cefdb34)).

keywords          : "ordinal regression, monte carlo simulations, power analysis"
wordcount         : "6987"
bibliography:
  - "packages.bib"
  - "`r filor::fil()$bib`"
floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
params:
  floatplaceh: true
  preprint: true
classoption       : "man"
output: 
  papaja::apa6_pdf:
    latex_engine: xelatex
    header_includes:
      - \usepackage{booktabs, caption, longtable, colortbl, array, hhline, mathbf}
  papaja::apa6_docx: default
---

@@

We can identify three main models: *cumulative models* [CM, @Agresti2010-rz;  @McCullagh1980-cw], *sequential models* [@Tutz1990-fe], and *adjacent category models*. Among these, the CM is the most widely used, assuming the existence of a latent variable categorized using a set of thresholds. The *sequential model* is appropriate when modeling sequential processes where responding to a certain category implies have already reached lower categories. The *adjacent category model* compares a category with the successive one and can be seen  the adjacent-category model can be seen as a series of binomial regressions taking into account the ordering [@Tutz2022-dg].

@@

In this section we introduce some notation for the CM to be consistent with the existing literature and the `ordinal` R package. We define $Y_k$ as the observed ordinal variable with $k$ levels and $Y^\star$ is the underlying latent variable. The latent variable is segmented using $k - 1$ thresholds $\alpha_1, \dots, \alpha_{k - 1}$. Similarly to the generalized linear models framework [e.g., @Fox2015-ps], we define $g(p) = \eta$ as the link function that maps probabilities into the linear predictor $\eta$. To transform back $\eta$ into probabilities we use the inverse of the link function $p = g^{-1}(\eta)$. The specific link function define the type of model and require different R functions. For example, using a Normal distribution (*probit* link function) requires using the cumulative distribution function $g(p) = \Phi^{-1}(p) = \eta$ and the inverse of the link function is the inverse cumulative distribution function (or quantile function) defined $p = g^{-1}(\eta) = \Phi(\eta)$.

@@

In the CM, thresholds $\alpha_k$ are considered fixed and part of the measurement procedure [@Liddell2018-wu; but see the *location-shift* models by @Tutz2022-dg, where thresholds vary as a function of predictors] and can be considered as intercepts. The proposed CM can be parametrized in different ways. @Liddell2018-wu proposed a Bayesian version of the model and @Gelman2020-tg proposed other thresholds parametrizations.

@@

For fitting the CM we used the `ordinal` package [@Christensen2023-yi]. The `ordinal` package provide a complete and intuitive way to implement the ordinal models. The syntax is very similar to standard linear models in R with functions to calculate predictions, perform model comparison and extract relevant model information.[^2]

[^2]: For a very complete overview of the ordinal package see <https://cran.r-project.org/web/packages/ordinal/ordinal.pdf> and <https://cran.uni-muenster.de/web/packages/ordinal/vignettes/clm_article.pdf>

@@

```{r tab-dataset-example-latex, eval = which_output("latex")}
ss |> 
  kable(booktabs = TRUE, format = "latex", caption = filor::get_caption(), escape = FALSE, align = "c", row.names = FALSE) |> 
  kable_styling(full_width = FALSE, latex_options = c("scale_down")) |> 
  row_spec(0, bold = TRUE)
```

@@

```{r fig-effects-num-by-cat-interaction, fig.place = TRUE, fig.width=7, fig.height=12, fig.cap=filor::get_caption()}
# plot(ggpredict(fit, terms = c("x[all]", "g")))
ggpredict(fit, terms = c("x[all]", "g")) |> 
  data.frame() |>
  mutate(response.level = paste("Y = ", response.level)) |> 
  ggplot(aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.3) +
  geom_line(aes(group = group), linewidth = 1) +
  facet_grid(response.level~.) +
  ylab("Probability") +
  mtheme() +
  viridis::scale_fill_viridis(discrete = TRUE)
```

### 2024-01-30 paper/paper.tex
update

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{ordinal, simulations, power\newline\indent Word count: X}
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Ordinal regression models made easy. A tutorial on parameter interpretation, data simulation, and power analysis.},
  pdfauthor={Filippo Gambarota1 \& Gianmarco Altoè1},
  pdflang={en-EN},
  pdfkeywords={ordinal, simulations, power},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Ordinal data are very common in psychology such as Likert items, ratings or generic ordered variables. Despite the widespread, these variables are usually analyzed using metric models (e.g., standard linear regression). This approach can have important drawbacks in terms of statistical inference (e.g., reduced power and increased type-1 error) and prediction. One of the possible reason of not using ordinal regression models could be the difficulty in understanding parameters (e.g., odds ratios) or conduting a power analysis. The aim of the tutorial is presenting ordinal regression models using a simulation-based approach. In the first section we introduced the general model highlighting the crucial components and assumptions. Then we explained how to intepret the parameters for a logit and probit model. Then we proposed two way for simulating ordinal data as a function of predictors showing common research design such as a 2x2 interaction with categorical predictors and the interaction between a numeric and categorical predictor. Finally, we showed an example of power analysis using simulations that can be easily extended to complex models with multiple predictors. The tutorial is supported by a collection of custom R functions developed to simulate and understand ordinal regression models. The code to reproduce the proposed simulation, the custom R functions and other examples of ordinal regression models can be found on the online Open Science Framework repository (\href{https://osf.io/93h5j/?view_only=33f262ee28374a88b935f0a25cefdb34}{https://osf.io/93h5j}).
}

@@

We can identify three main models: \emph{cumulative models} (Agresti, 2010; CM, McCullagh, 1980), \emph{sequential models} (Tutz, 1990), and \emph{adjacent category models}. Among these, the CM is the most widely used, assuming the existence of a latent variable categorized using a set of thresholds. The \emph{sequential model} is appropriate when modeling sequential processes where responding to a certain category implies have already reached lower categories. The \emph{adjacent category model} compares a category with the successive one and can be seen the adjacent-category model can be seen as a series of binomial regressions taking into account the ordering (Tutz, 2022).

@@

In this section we introduce some notation for the CM to be consistent with the existing literature and the \texttt{ordinal} R package (Christensen, 2022). We define \(Y_k\) as the observed ordinal variable with \(k\) levels and \(Y^\star\) is the underlying latent variable. The latent variable is segmented using \(k - 1\) thresholds \(\alpha_1, \dots, \alpha_{k - 1}\). Similarly to the generalized linear models framework (e.g., Fox, 2015), we define \(g(p) = \eta\) as the link function that maps probabilities into the linear predictor \(\eta\). To transform back \(\eta\) into probabilities we use the inverse of the link function \(p = g^{-1}(\eta)\). The specific link function define the type of model and require different R functions. For example, using a Normal distribution (\emph{probit} link function) requires using the cumulative distribution function \(g(p) = \Phi^{-1}(p) = \eta\) and the inverse of the link function is the inverse cumulative distribution function (or quantile function) defined \(p = g^{-1}(\eta) = \Phi(\eta)\).

@@

In the CM, thresholds \(\alpha_k\) are considered fixed and part of the measurement procedure (Liddell \& Kruschke, 2018; but see the \emph{location-shift} models by Tutz, 2022, where thresholds vary as a function of predictors) and can be considered as intercepts. The proposed CM can be parametrized in different ways. Liddell and Kruschke (2018) and Kruschke (2015) proposed a Bayesian version of the model and Gelman, Hill, and Vehtari (2020) proposed other thresholds parametrizations.

@@

For fitting the CM we used the \texttt{ordinal} package (Christensen, 2019). The \texttt{ordinal} package provide a complete and intuitive way to implement the ordinal models. The syntax is very similar to standard linear models in R with functions to calculate predictions, perform model comparison and extract relevant model information.\footnote{For a very complete overview of the ordinal package see Christensen (2019) and the Package documentation \url{https://cran.r-project.org/web/packages/ordinal/ordinal.pdf}}

@@

\begin{table}
\centering
\caption{\label{tab:tab-dataset-example-latex}Summary of the simulated dataset. For each group (a and b) we reported mean, median and standard deviation of the ordinal outcome (metric descriptive statistics). For each ordinal outcome (\(Y\)) we reported the frequency and (within parentheses) the probability.}
\centering
\begin{tabular}[t]{cccccccc}
\toprule
\textbf{Group} & \textbf{Mean} & \textbf{Median} & \textbf{SD} & \textbf{Y1} & \textbf{Y2} & \textbf{Y3} & \textbf{Y4}\\
\midrule
a & 2.5 & 2 & 1.1 & \textbf{599} (p = \textit{11.98}) & \textbf{662} (p = \textit{13.24}) & \textbf{627} (p = \textit{12.54}) & \textbf{612} (p = \textit{12.24})\\
b & 3.17 & 3.5 & 0.99 & \textbf{221} (p = \textit{4.42}) & \textbf{381} (p = \textit{7.62}) & \textbf{648} (p = \textit{12.96}) & \textbf{1250} (p = \textit{25})\\
\bottomrule
\end{tabular}
\end{table}

@@

\bibitem[\citeproctext]{ref-Christensen2019-cz}
Christensen, R. H. B. (2019). \emph{Ordinal---regression models for ordinal data}.

\bibitem[\citeproctext]{ref-Christensen2022-jk}
Christensen, R. H. B. (2022). \emph{Ordinal---regression models for ordinal data}.

@@

\bibitem[\citeproctext]{ref-Fox2015-ps}
Fox, J. (2015). \emph{Applied regression analysis and generalized linear models}. SAGE Publications. Retrieved from \url{https://play.google.com/store/books/details?id=BlsKogEACAAJ}

@@

\bibitem[\citeproctext]{ref-Kruschke2015-re}
Kruschke, J. K. (2015). \emph{Doing bayesian data analysis}. \url{https://doi.org/10.1016/c2012-0-00477-2}

@@

\bibitem[\citeproctext]{ref-Likert1932-xw}
Likert, R. (1932). A technique for the measurement of attitudes. \emph{Archives of Psychology}, \emph{22}, 55. Retrieved from \url{https://psycnet.apa.org/record/1933-01885-001}

@@

\bibitem[\citeproctext]{ref-Overgaard2021-hs}
Overgaard, M., \& Sandberg, K. (2021). The perceptual awareness scale---recent controversies and debates. \emph{Neuroscience of Consciousness}. Retrieved from \url{https://academic.oup.com/nc/article-pdf/doi/10.1093/nc/niab044/41765024/niab044.pdf}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{ordinal regression, monte carlo simulations, power analysis\newline\indent Word count: 6987}
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Ordinal regression models made easy. A tutorial on parameter interpretation, data simulation, and power analysis.},
  pdfauthor={Filippo Gambarota1 \& Gianmarco Altoè1},
  pdflang={en-EN},
  pdfkeywords={ordinal regression, monte carlo simulations, power analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Ordinal data are widespread in psychology such as Likert items, ratings, or generic ordered variables. These variables are usually analyzed using metric models (e.g., standard linear regression) with important drawbacks in terms of statistical inference (reduced power and increased type-1 error) and prediction. One possible reason for not using ordinal regression models could be difficulty in understanding parameters or conducting a power analysis. The tutorial aims to present ordinal regression models using a simulation-based approach. Firstly, we introduced the general model highlighting crucial components and assumptions. Then we explained how to interpret parameters for a logit and probit model. Then we proposed two ways for simulating data as a function of predictors showing a 2x2 interaction with categorical predictors and the interaction between a numeric and categorical predictor. Finally, we showed an example of power analysis using simulations that can be easily extended to complex models with multiple predictors. The tutorial is supported by a collection of custom R functions developed to simulate and understand ordinal regression models. The code to reproduce the proposed simulation, the custom R functions, and additional examples of ordinal regression models can be found on the online Open Science Framework repository (\href{https://osf.io/93h5j/?view_only=33f262ee28374a88b935f0a25cefdb34}{https://osf.io/93h5j}).
}

@@

We can identify three main models: \emph{cumulative models} (CM, Agresti, 2010; McCullagh, 1980), \emph{sequential models} (Tutz, 1990), and \emph{adjacent category models}. Among these, the CM is the most widely used, assuming the existence of a latent variable categorized using a set of thresholds. The \emph{sequential model} is appropriate when modeling sequential processes where responding to a certain category implies have already reached lower categories. The \emph{adjacent category model} compares a category with the successive one and can be seen the adjacent-category model can be seen as a series of binomial regressions taking into account the ordering (Tutz, 2022).

@@

In this section we introduce some notation for the CM to be consistent with the existing literature and the \texttt{ordinal} R package. We define \(Y_k\) as the observed ordinal variable with \(k\) levels and \(Y^\star\) is the underlying latent variable. The latent variable is segmented using \(k - 1\) thresholds \(\alpha_1, \dots, \alpha_{k - 1}\). Similarly to the generalized linear models framework (e.g., Fox, 2015), we define \(g(p) = \eta\) as the link function that maps probabilities into the linear predictor \(\eta\). To transform back \(\eta\) into probabilities we use the inverse of the link function \(p = g^{-1}(\eta)\). The specific link function define the type of model and require different R functions. For example, using a Normal distribution (\emph{probit} link function) requires using the cumulative distribution function \(g(p) = \Phi^{-1}(p) = \eta\) and the inverse of the link function is the inverse cumulative distribution function (or quantile function) defined \(p = g^{-1}(\eta) = \Phi(\eta)\).

@@

In the CM, thresholds \(\alpha_k\) are considered fixed and part of the measurement procedure (Liddell \& Kruschke, 2018; but see the \emph{location-shift} models by Tutz, 2022, where thresholds vary as a function of predictors) and can be considered as intercepts. The proposed CM can be parametrized in different ways. Liddell and Kruschke (2018) proposed a Bayesian version of the model and Gelman, Hill, and Vehtari (2020) proposed other thresholds parametrizations.

@@

For fitting the CM we used the \texttt{ordinal} package (Christensen, 2023). The \texttt{ordinal} package provide a complete and intuitive way to implement the ordinal models. The syntax is very similar to standard linear models in R with functions to calculate predictions, perform model comparison and extract relevant model information.\footnote{For a very complete overview of the ordinal package see \url{https://cran.r-project.org/web/packages/ordinal/ordinal.pdf} and \url{https://cran.uni-muenster.de/web/packages/ordinal/vignettes/clm_article.pdf}}

@@

\begin{table}
\centering
\caption{\label{tab:tab-dataset-example-latex}Summary of the simulated dataset. For each group (a and b) we reported mean, median and standard deviation of the ordinal outcome (metric descriptive statistics). For each ordinal outcome (\(Y\)) we reported the frequency and (within parentheses) the probability.}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{cccccccc}
\toprule
\textbf{Group} & \textbf{Mean} & \textbf{Median} & \textbf{SD} & \textbf{Y1} & \textbf{Y2} & \textbf{Y3} & \textbf{Y4}\\
\midrule
a & 2.5 & 2 & 1.1 & \textbf{599} (p = \textit{11.98}) & \textbf{662} (p = \textit{13.24}) & \textbf{627} (p = \textit{12.54}) & \textbf{612} (p = \textit{12.24})\\
b & 3.17 & 3.5 & 0.99 & \textbf{221} (p = \textit{4.42}) & \textbf{381} (p = \textit{7.62}) & \textbf{648} (p = \textit{12.96}) & \textbf{1250} (p = \textit{25})\\
\bottomrule
\end{tabular}}
\end{table}

@@

\bibitem[\citeproctext]{ref-Christensen2023-yi}
Christensen, R. H. B. (2023). \emph{Ordinal---regression models for ordinal data}. Retrieved from \url{https://CRAN.R-project.org/package=ordinal}

@@

\bibitem[\citeproctext]{ref-Fox2015-ps}
Fox, J. (2015). \emph{Applied regression analysis and generalized linear models}. SAGE Publications.

@@

@@

\bibitem[\citeproctext]{ref-Likert1932-xw}
Likert, R. (1932). A technique for the measurement of attitudes. \emph{Archives of Psychology}, \emph{22}, 55.

@@

\bibitem[\citeproctext]{ref-Overgaard2021-hs}
Overgaard, M., \& Sandberg, K. (2021). The perceptual awareness scale---recent controversies and debates. \emph{Neuroscience of Consciousness}. \url{https://doi.org/10.1093/nc/niab044/41765024/niab044}
